Location Classification on Tweets

### 2016-03-10 docs/paper.tex
abstract revisited

We extracted textual features that hint to a user's location by comparing different methods. Unlike some of the previous studies, we have only used individual tweet texts, geolocation of those tweets and simplified the question to a binary classification problem. Our results are showing up to 74\% recall rates.

% Previous research on Twitter user location classification is mostly focusing on multi-class prediction. Approaching at the same problem from another perspective, in some cases, it may be enough to answer if someone belongs to a location or not. In this perspective, we have compared some models for predicting tweet locations using Binary and Multi-Class Classification. We have seen that if the problem at hand is reducible to Binary Classification, it is possible to make much better predictions.

@@

Using similar features, previous research tries to determine the geolocation of a tweet using multi-class classification algorithms. These methods are trying to determine the most likely geolocation for a tweet from a list(e.g. cities in a country). It is sometimes hard to do that, because we need data from all cities. Also the algorithms and the implementations become more complicated. Thus, in cases where we just want to know if someone is within a state/city/borough, this approach becomes unnecessarily heavy. In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet sent within the boundaries of a location(i.e. Manhattan, NY).

>>>>

We extracted textual features from tweets which hint to the location it was sent from. Unlike some of the previous studies, we have only used individual tweet texts and geolocation of those tweets. We have also simplified the question to a binary classification problem. Our results are showing up to 74\% recall rates in classifying if a tweet is sent from Manhattan, NY.

@@

Using similar features, previous research tries to determine the geolocation of a tweet using multi-class classification algorithms. These methods are trying to determine the most likely geolocation for a tweet from a list(e.g. cities in a country). It is sometimes hard to do that, because we need data from all cities. Also the algorithms and the implementations become more complicated. Thus, in cases where we just want to know if someone is within a state/city/borough, this approach becomes unnecessarily heavy. In this research, we are simplifying this problem by using binary classification algorithms, which are trying to determine if a tweet is sent within the boundaries of a location(i.e. Manhattan, NY).
